### 2017-09-11 monograph/thesis/chapters/introduction.tex
Replaced out of date bibtex with the updated biblatex package for
bibliography references.
Created the references.bib languageIndependentFramework key.
Created the references architectureFormatting and prettyPrinting on
monograph/thesis/references.bib and pointed some random paragraphs
citing them on monograph/thesis/chapters/introduction.tex

\chooselang
{
    % TODO, put reference for this
    Questions like ``What are good programming practices?'' Or ``Why are these practices are good?''
    Are not easy to answer. But each programmer learns to write their codes in a certain way, with
    certain features like using 4 or 8 spaces to indent lines, always leave a blank line before each
    control structure as if or for statements, and alike rules.

    % TODO, put reference for this
    But entering the universe of good practices, there are many things for discoursing. So in this
    work implementation tool called `Object Beautifier' specifically dedicates on how to perform
    the best layout/display of programming code on the computer screen, so that maximize and
    facilitate the understanding of same. Therefore, allowing the programmer to disperse more tempe
    thinking about its coding algorithms problem, other than trying to decipher the information that
    is presented to it on the screen through infinit different code layouts.

    % TODO, put reference for this
    Within this work\s area, we need to also think long and hard about how to share the programming
    code of the programmers among you. Now, the problem of human diversity, like all big scientific
    questions -- how do you explain something like that -- It can be broken down into sub-questions.
    It happens many times, which is a good practice for a `Programmer A', is not the same to another
    `Programmer B'. For example, imagine some code where a programmer decided to put before each
    `if' statement, a blank line. It is therefore expected that whenever we see a blank line we can
    potentially find a matching `if', which can be considered a quite useful pattern matching as
    empty line may call better your attention.

    % TODO, put reference for this
    But again this is something heavily dependent of what each one learning through their life time.
    Imagine another programmer do not liked this rule, and when he was writing your code involving
    an `if', he did not put such blank line another programmer is expecting. So when the first
    programmer start reading its the code and look for `if', he will be expecting for blank lines
    before its if\s. But will lose some time searching until realize another programmer does not put
    them, or perhaps he forgot to insert them.

    % TODO, put reference for this
    These differences are due to the diversity of ways we learn programming, i.e., to the ways we
    are used to doing coding, as much as the abilities and objectives of every programmer developed.
    Hence, nowadays it becomes a big problem because we increasingly need more and more programmers
    working together developing several and diverse computing systems. Where the latter is due to
    the fact of the complexity of computer systems growing increasingly, therefore over requiring
    programmers working and sharing their codes and ideas.

@@

        \item Propose a unique tool that allowing several and distinct programming `best practices'
        being implemented in several programming languages, which can be configured and set
        accordingly to their wishes.
    \end{enumerate}

>>>>

\chooselang
{
    % TODO, put reference for this
    Questions like ``What are good programming practices?'' Or ``Why are these practices are
    good?''Are not easy to answer. But each programmer learns to write their codes in a certain way,
    with certain features like using 4 or 8 spaces to indent lines, always leave a blank line before
    each control structure as if or for statements, and alike rules. \cite{industrialApplication}

    % TODO, put reference for this
    But entering the universe of good practices, there are many things for discoursing. So in this
    work implementation tool called `Object Beautifier' specifically dedicates on how to perform the
    best layout/display of programming code on the computer screen, so that maximize and facilitate
    the understanding of same. Therefore, allowing the programmer to disperse more tempe thinking
    about its coding algorithms problem, other than trying to decipher the information that is
    presented to it on the screen through infinit different code layouts. \cite{programIndentation}

    % TODO, put reference for this
    Within this work\s area, we need to also think long and hard about how to share the programming
    code of the programmers among you. Now, the problem of human diversity, like all big scientific
    questions -- how do you explain something like that -- It can be broken down into sub-questions.
    It happens many times, which is a good practice for a `Programmer A', is not the same to another
    `Programmer B'. For example, imagine some code where a programmer decided to put before each
    `if' statement, a blank line. It is therefore expected that whenever we see a blank line we can
    potentially find a matching `if', which can be considered a quite useful pattern matching as
    empty line may call better your attention. \cite{independentFramework}

    % TODO, put reference for this
    But again this is something heavily dependent of what each one learning through their life time.
    Imagine another programmer do not liked this rule, and when he was writing your code involving
    an `if', he did not put such blank line another programmer is expecting. So when the first
    programmer start reading its the code and look for `if', he will be expecting for blank lines
    before its if\s. But will lose some time searching until realize another programmer does not put
    them, or perhaps he forgot to insert them. \cite{architectureFormatting}

    % TODO, put reference for this
    These differences are due to the diversity of ways we learn programming, i.e., to the ways we
    are used to doing coding, as much as the abilities and objectives of every programmer developed.
    Hence, nowadays it becomes a big problem because we increasingly need more and more programmers
    working together developing several and diverse computing systems. Where the latter is due to
    the fact of the complexity of computer systems growing increasingly, therefore over requiring
    programmers working and sharing their codes and ideas. \cite{prettyPrinting}

@@

        \item Propose a unique tool that allowing several and distinct
        programming `best practices'being implemented in several programming languages, which can be
        configured and set accordingly to their wishes.
    \end{enumerate}
